---
title: "Predicitve"
author: "Srajan Rai"
date: "11/20/2019"
output:
  html_document: default
  word_document: default
---
## Import the House dataset and load few packages 
```{r,warning=FALSE,message=FALSE}
House<-read.csv("/Users/apple/Documents/UCD/sem1/Predictive analytics/assignments/House.csv")
library(GGally)
library(car)
library(olsrr)
```
## EDA
#### BoxPlot,Histogram, Summary of House Sale Price
1. Gives the Boxplots, Histogram and summary for the Sale price of Houses
```{r}
#For the summary
summary(House$Price)
#Box plot
boxplot(House$Price)
#Histogram
hist(House$Price)
```

#### 2- categorical variables to factors
Convert Categorical variables into factors
```{r}
House$Bath<-factor(House$Bath)
House$Bed<-factor(House$Bed)
House$Garage<-factor(House$Garage)
House$School<-factor(House$School)
```

#### Summary and  Boxplot describing how sales price varies with  respect to the number of bedrooms, bathrooms, garage size  and school. 
```{r,warning=FALSE}
attach(House)
boxplot(Price~House$Bed)
by(Price,Bed,summary)

boxplot(Price~House$Bath)
by(Price,Bath,summary)

boxplot(Price~House$Garage)
by(Price,Garage,summary)

boxplot(Price~House$School)
by(Price,School,summary)

```

#### 3-Correlation, Pairs plot
Gives an idea about the variables if they correlated or not 
```{r,warning=FALSE}
pairs(Price~Size+Year+Lot)
cor(House[c(1,2,3,6)])
```

<!-- To avoid the intercept being negative the numerical variables are substracted from their mean values -->
```{r}
House$Lot<-House$Lot-mean(House$Lot)
House$Year<-House$Year-mean(House$Year)
House$Size<-House$Size-mean(House$Size)

```


## Regression model
### Multiple Linear regression model
```{r}
mod<-lm(Price~Lot+Size+Year+Bath+Bed+Garage+School,data=House)
summary(mod)
plot(mod)
```
## Anova 
### Type 1 anova and non-significant predictor variable (Year) is removed
```{r}
anova(mod)
mod2<-lm(Price~Lot+Size+Bath+Bed+Garage+School,data = House)

```

### Type 2 anova
```{r}
Anova(mod,mod2)
```


## Diagnostics:
### 1-Added variable plot and component plus residual plot
```{r}
avPlots(mod)
crPlots(mod)
```
### 2-Durbin-Watson test
```{r}
dwt(mod)
```
# 3-Collinearity Check-variation inflation factor
```{r}
vif(mod)
```
### 4-Zero conditional mean and homoscedasticity
```{r}
plot(fitted(mod),rstudent(mod))
abline(h=0)

par(mfrow=c(4,2))
plot(House$Size,rstudent(mod))
plot(House$Lot,rstudent(mod))
plot(House$Year,rstudent(mod))
plot(House$Bed,rstudent(mod))
plot(House$Bath,rstudent(mod))
plot(House$Garage,rstudent(mod))
plot(House$School,rstudent(mod))
```

### 5-Normality Assumption 
```{r}
hist(rstudent(mod))
qqnorm(rstudent(mod))
qqline(rstudent(mod),col=2)
```


## Leverage, Influence and Outliers:
### Leverage values and Leverage plots
```{r}

lev_point<-as.numeric(which(hatvalues(mod)>((2*7)/76)))
lev_point
leveragePlots(mod)
```

### 2- influencial Plot
```{r}

influencePlot(mod, main="Influence Plot",sub="Circle size is proportial to Cook’s Distance")
ols_plot_cooksd_bar(mod)
```

### Outlier
```{r}
outlierTest(mod)
ols_plot_resid_lev(mod)
```
### Outliers treated and model built 
```{r}
n1<-House
n1<-n1[-c(44),]
n1<-n1[-c(30),]
n1<-n1[-c(25),]
n1<-n1[-c(15),]
n1<-n1[-c(32),]
n1<-n1[-c(32),]

modd<-lm(Price~Lot+Size+Year+Bed+Bath+Garage+School,data = n1)
outlierTest(modd)
ols_plot_cooksd_bar(modd)
ols_plot_resid_lev(modd)
```

```{r}

ci=predict(mod,level=0.95,interval='confidence')

pi=predict(mod,level=0.95,interval='prediction')

cipiplot = ggplot(House, aes(House$Price,pi[,1])) + geom_point() + geom_smooth(method=lm,aes(color="Regression Line")) + geom_line(aes(y=pi[,2], color="Prediction Interval")) +geom_line(aes(y=ci[,2], color="Confidence Interval"))+geom_line(aes(y=ci[,3], color="Confidence Interval")) + geom_line(aes(y=pi[,3], color="Prediction Interval")) + labs(x="Observed Price", y="Expected Price")+scale_color_manual(values = c("red","blue","black"))+ggtitle("With Outliers")


cinew=predict(modd,level=0.95,interval='confidence')

pinew=predict(modd,level=0.95,interval='prediction')

cipiplotnew = ggplot(n1, aes(n1$Price,pinew[,1])) + geom_point() + geom_smooth(method=lm,aes(color="Regression Line")) + geom_line(aes(y=pinew[,2], color="Prediction Interval")) +geom_line(aes(y=cinew[,2], color="Confidence Interval"))+geom_line(aes(y=cinew[,3], color="Confidence Interval")) + geom_line(aes(y=pinew[,3], color="Prediction Interval")) + labs(x="Observed Price", y="Expected Price")+scale_color_manual(values = c("red","blue","black"))+ggtitle("With out Outliers")
cipiplotnew
cipiplot
```
